---
title: "Northwest Universities R Day 2018 - Pub Quiz"
author: "Northwest Universities R Day Organisers"
date: "31 October 2018"
output:
  html_document:
    css: "style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## I see dead people

### Question 1

Where do the remains of R. A Fisher lie?

```{r}
print("St Peter’s Cathedral, Adelaide, Adelaide City, South Australia, Australia")
```

### Question 2

What deceased statistician said "All models are wrong but some are useful"?

```{r}
print("George Box")
```

### Question 3

What deceased person is credited with first using the term "regression" to describe the relationship between two variables?

```{r}
print("Francis Galton")
```

### Question 4

What well-known company hired the (now deceased), pseudonymous “Student” (a.k.a. William Sealy Gosset) in 1899?

```{r}
print("Guinness")
```

### Question 5

What famous female historical figure is credited with innovative use of information graphics, like the polar area diagram?

```{r}
print("Florence Nightingale")
```

## R-related questions

#### Question 6

Which one of these data sets is not in the R `datasets` package:

- `ldeaths` (Monthly Deaths from Lung Diseases in the UK)
- `USArrests` (Violent Crime Rates by US State)
- `gapminder` (Excerpt of the Gapminder data on life expectancy, GDP per capita, and population by country)
- `HairEyeColor` (Hair and Eye Color of Statistics Students)

### Question 7

If you get the error

```
Error in rcorr() : could not find function "rcorr"
```

which package have you forgotten to load?

### Question 8

What colour is your chart background if you use `theme_excel()` from the `ggthemes` package?

## Some coding questions

### Question 9

Write code to reproduce the graphic below.

### Question 10

Match the following codes with their result.

#### Codes

- `10 %% 2`
- `1:10 * 2`
- `1:10%%2`
- `1:10 * 2 %% 2`
- `1:(10 * 2)`
- `11 %% 2`

#### Result

- `r 10 %% 2`
- `r 1:10 * 2`
- `r 1:10%%2`
- `r 1:10 * 2 %% 2`
- `r 1:(10 * 2)`
- `r 11 %% 2`

## Tie breaker

Make the best coloured version of plot 4b
