---
title: "Northwest Universities R Day 2018 - Pub Quiz"
author: "Northwest Universities R Day Organisers"
date: "31 October 2018"
output:
  html_document:
    css: "style.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## I see dead people

### Question 01

Where do the remains of R. A Fisher lie?

```{r}
print("St Peter’s Cathedral, Adelaide, Adelaide City, South Australia, Australia")
```

### Question 02

What deceased statistician said "All models are wrong but some are useful"?

```{r}
print("George Box")
```

### Question 03

What deceased person is credited with first using the term "regression" to describe the relationship between two variables?

```{r}
print("Francis Galton")
```

### Question 04

What well-known company hired the (now deceased), pseudonymous “Student” (a.k.a. William Sealy Gosset) in 1899?

```{r}
print("Guinness")
```

### Question 05

What famous female historical figure is credited with innovative use of information graphics, like the polar area diagram?

```{r}
print("Florence Nightingale")
```

## The R-things

### Question 06

What is the name of the town in England North West starts with R and has a twinning city/town?

```{r}
print("Rochdale")
```

### Question 07

What is the name of one of the Economics Nobel laureates who surname starts with R?

```{r}
print("Paul Romer")
```

### Question 08

On the TV show "Buffy, the Vampire Slayer", which run between 1996 and 2003, what is the name of  Buffy Summers' teacher and mentor?

```{r}
print("Rupert Giles")
```

### Question 09

What is the name of the captain of the boat which picked up Victor in Mary Shelley famous book "The Modern Prometheus", also know as "Frankenstein".

```{r}
print("Captain Robert Walton")
```

### Question 10

What is the name of the English inventor best known for designing a drop box to improve the capability of weaving looms and son of John Kay?

```{r}
print("Robert Kay")
```

## R-related questions

#### Question 6

Which one of these data sets is not in the R `datasets` package:

- `ldeaths` (Monthly Deaths from Lung Diseases in the UK)
- `USArrests` (Violent Crime Rates by US State)
- `gapminder` (Excerpt of the Gapminder data on life expectancy, GDP per capita, and population by country)
- `HairEyeColor` (Hair and Eye Color of Statistics Students)

### Question 7

If you get the error

```
Error in rcorr() : could not find function "rcorr"
```

which package have you forgotten to load?

### Question 8

What colour is your chart background if you use `theme_excel()` from the `ggthemes` package?

## Some coding questions

### Question 9

Write code to reproduce the graphic below.

### Question 10

Match the following codes with their result.

#### Codes

- `10 %% 2`
- `1:10 * 2`
- `1:10%%2`
- `1:10 * 2 %% 2`
- `1:(10 * 2)`
- `11 %% 2`

#### Result

- `r 10 %% 2`
- `r 1:10 * 2`
- `r 1:10%%2`
- `r 1:10 * 2 %% 2`
- `r 1:(10 * 2)`
- `r 11 %% 2`

## Tie breaker

Make the best coloured version of plot 4b
